---
title: "Surgery Risk Prediction Report"
output: html_document
params:
  n: 5
  patientName: Patient Name
  MRN: AA12345678
  physician: Ira Leeds, MD
  baselineComplications: 13.6
  majorComplications: 18.6
  deathRisk: 1.0
  newDF : NA
---

Patient Name: `r params$patientName` <br />
MRN: `r params$MRN` <br />
Physician: `r params$physician` <br />
Report Generated: `r format(Sys.time(), '%B %d, %Y')`

-----
This is your individualized surgery risk report based on the information you and your physician entered. <br />

**Baseline Major Complication Risk:** `r params$baselineComplications`% <br />
  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;*This is your risk of a major complication based on factors that you cannot change, such as you chronic conditions.*

**Your Current Major Complication Risk:** `r params$majorComplications`% <br />
  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;*This is your risk of a major complication based on all factors, including modifiable risk factors*
  
**Your Current Risk of Death:** `r params$deathRisk`% <br />
  &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;*This is your risk of death during your surgery*


<br /><br /><br />
**Modifiable Risk Factors:**<br />
The following risk factors are increasing your risk of a major complication:

```{r, dfRiskChanges, echo=FALSE, results='show', message=TRUE}
txt <-
if(dfRiskChanges[,'Funcational'] != -1)
  txt <- paste0("Your functional status is impacting your risk by +",
                formatC(dfRiskChanges[,'Funcational']*-1,
                        digits = 1,
                        format = "f"),
                "%")
txt

  
  
  
  
  #   if(dfRiskChanges[,'Steroid'] != -1) {#if steroids == yes
  # if(dfMaster[1, 'HxCHF'] == 1) {#if CHF status == yes
  # if(dfMaster[1, 'SOB'] == 1) {#if SOB status == yes
  # if(dfMaster[1, 'HxCOPD'] == 1) {#if COPD status == yes
  # if(dfMaster[1, 'Smoker'] == 1) {#if Smoking status == yes
  # if(dfMaster[1, 'DMAll'] == 1) {#if diabetic status == yes
  # if(dfMaster[1, 'HTNMed'] == 1) {#if Smoking status == yes
  # if(dfMaster[1, 'BMI'] > 25) {

  
  
  
  
  
```


<br /><br /><br /><br /><br /><br /><br />

```{r pp1, echo=FALSE, results='show', message=TRUE}
pp1
```

A plot of `params$n` random points.

```{r}
plot(rnorm(params$n), rnorm(params$n))
```